---
title: "Tutorial7_Alternate"
subtitle: "ETC1000"
---

{{< include _extensions/r-wasm/live/_knitr.qmd >}}

## About

For those of you who have yet to install R and RStudio, you can still complete the exercises using the document here. Note: this is not the same as having R and RStudio installed on your laptop, so you should make it a priority to install these before the next class.

## Tutorial Demonstration

### 1. Reading data and assigning names

Use the `read.csv()` function to load the **Crime_data.csv** file. Then assign it (`<-`) to `crime`.

```{webr}

```


::: {.callout-important collapse="true"}
## Check Answer

```{r}
#| eval: false
crime <- read.csv("Crime_data.csv")
```
:::

### 2. Loading packages

Use the `library()` function to load the `dplyr` and `ggplot2` packages. Note: you will need to have installed these first (using the `install.packages()` function). If you have already installed them, you just need to call them using `library()`.


```{webr}


```


::: {.callout-important collapse="true"}
## Check Answer

```{r}
#| eval: false
library(dplyr)
library(ggplot2)
```
:::

### 3. Inspecting the data

Use the `str()` function to inspect the structure of the **crime** dataframe.


```{webr}

```


::: {.callout-important collapse="true"}
## Check Answer

```{r}
#| eval: false
str(crime)
```
:::

### 4. Descriptive statistics

Obtain the `mean()`, `median()`, min() and `max()` for **Sentence**.


```{webr}

```


::: {.callout-important collapse="true"}
## Check Answer

```{r}
#| eval: false
crime |> 
  summarise(mean(Sentence),
            median(Sentence),
            min(Sentence),
            max(Sentence))
```
:::

### 5. Creating variables

Create a new variable called **Sentence_years** that converts the current **Sentence** variable (currently measured in months) into years (by dividing by 12). Then save this as a new dataframe called `crime2`.

```{webr}

```

::: {.callout-important collapse="true"}
## Check Answer

```{r}
#| eval: false
crime2 <- 
  crime |> 
  mutate(Sentence_years = Sentence/12)
```
:::

### 6. head()

Inspect the first 6 rows of the dataframe for both Sentence and Sentence_years using the `head()` function

```{webr}

```

::: {.callout-important collapse="true"}
## Check Answer

```{r}
#| eval: false
crime2$Sentence |> head()
crime2$Sentence_years |> head()
```
:::

### 7. Correlation

Use the `cor()` function to compute the correlation coefficient between **Sentence** and **EvidenceScore**.


```{webr}

```

::: {.callout-important collapse="true"}
## Check Answer

```{r}
#| eval: false
crime2 |> summarise(cor(Sentence, EvidenceScore))
```
:::

### 8. Selecting variables

Create a new dataframe that only contains **Sentence**, **EvidenceScore**, **PriorConvictions** and **N_witnesses**. Save this as a new dataframe called `small_data`.

```{webr}

```

::: {.callout-important collapse="true"}
## Check Answer

```{r}
#| eval: false
small_data <- 
  crime2 |> 
  select(Sentence, EvidenceScore, PriorConvictions, N_witnesses)
```
:::

### 9. Correlation Matrix

Use the cor function on the `small_data` you created in the previous question to generate a correlation matrix

```{webr}

```

::: {.callout-important collapse="true"}
## Check Answer

```{r}
#| eval: false
cor(small_data)
```
:::

### 10. Scatterplot

Use the `ggplot()` function to create a scatterplot with **EvidenceScore** as the x variable and **Sentence_years** as the y variable. Note: make sure you have loaded the `ggplot2` package (see Question 2).


```{webr}

```

::: {.callout-important collapse="true"}
## Check Answer

```{r}
#| eval: false
ggplot(crime2, aes(x = EvidenceScore, y = Sentence_years)) +
  geom_point()
```
:::

### 11. Boxplot

Use the `ggplot()` function to create a boxplot with **WeaponUsed** as the x variable and **Sentence_years** as the y variable. Note: make sure you have loaded the `ggplot2` package (see Question 2).


```{webr}

```

::: {.callout-important collapse="true"}
## Check Answer

```{r}
#| eval: false
ggplot(crime2, aes(x = WeaponUsed, y = Sentence_years)) +
  geom_boxplot()
```
:::

### 12. Histogram

Use the `ggplot()` function to create a histogram with **Sentence_years** as the x variable. Note: make sure you have loaded the `ggplot2` package (see Question 2).


```{webr}

```

::: {.callout-important collapse="true"}
## Check Answer

```{r}
#| eval: false
ggplot(crime2, aes(x = Sentence_years)) +
  geom_histogram()
```
:::

### 13. Contingency tables

Use the `table()` function to create a contingency table with **Location** as the rows and **WeaponUsed** as the columns.


```{webr}

```

::: {.callout-important collapse="true"}
## Check Answer

```{r}
#| eval: false
table(Location = crime2$Location, 
      WeaponUsed = crime2$WeaponUsed)
```
:::

### 14. Proportions for contingency tables

Wrap the `prop.table()` function around your previous code to convert the counts to percentages. 


```{webr}

```

::: {.callout-important collapse="true"}
## Check Answer

```{r}
#| eval: false
prop.table(
  table(Location = crime2$Location, 
      WeaponUsed = crime2$WeaponUsed)
)
```
:::

### 15. Conditional Probability (Rows)

Add the `margin = 1` argument to your previous code to convert the proportions to conditional probabilities (conditional on the row variable).


```{webr}

```

::: {.callout-important collapse="true"}
## Check Answer

```{r}
#| eval: false
prop.table(
  table(Location = crime2$Location, 
      WeaponUsed = crime2$WeaponUsed),
  margin = 1
)
```
:::

### 16. Conditional Probability (Columns)

Change the `margin = 1` argument to `margin = 2` to update the table to show the conditional probability, conditional on the column variable.


```{webr}

```

::: {.callout-important collapse="true"}
## Check Answer

```{r}
#| eval: false
prop.table(
  table(Location = crime2$Location, 
      WeaponUsed = crime2$WeaponUsed),
  margin = 2
)
```
:::

## Exercise 6 (2.5%)

Now log into Moodle in complete the Exercise in the Week 7 folder. Make sure you don't close this document, as the first half of the questions will rely on what you have just completed. For those that do not have R/RStudio installed, you can use the code chunk spaces below to obtain your answers. Feel free to use as many/few as you wish.

```{webr}

```

```{webr}

```

```{webr}

```

```{webr}

```

```{webr}

```

```{webr}

```

```{webr}

```

```{webr}

```

```{webr}

```






